Trends of SDR in Thessaloniki

### 2023-06-29 Article.tex
Commit 2023-06-29 12:17

The shortwave downward solar irradiance (SDR) at the Earth's surface
plays a significant role, on Earths climate. Changes of the SDR can be
related to major changes on factors affecting the radiative forcing
balance and human activities. Multiple studies attempt to evaluate the
phenomenon and the potential causes
\citep{Ohvril2009, Schwarz2020, Wild2009, Wild2012, Xia2007, Zerefos2009}.
Although, there is regional variation of SDR, with both positive and
negative trends, most of the studies agree that the major factors are
the interaction of aerosols and clouds.

@@

A manual screening is performed, to remove inconsistencies and erroneous
recordings, that can occur randomly or systematically, during the long
continuous operation of the instrument. The manual screening is aided by
a radiation data quality assurance procedure, adjusted for this site,
based on methods of Long and
Shi~\citetext{\citeyear{long_automated_2008}; \citeyear{Long2006}}.
Thus, problematic recordings have been excluded from further processing.
Although it is not possible to detect all the bad data, the large number
of data and the aggregation scheme we use, can provide us with accurate
radiometric measurements, for the scope of this study.

@@

Due to a significant measurement uncertainty near, the horizon, we have
to exclude all measurements with SZA greater than \(85^\circ\).
Moreover, due to some obstructions around the site (hills and
buildings), we excluded data with Azimuth angle between \(35^\circ\) and
\(120^\circ\) with SZA greater than \(80^\circ\). On the latter
instances, Sun is systematically, not visible by the instrument's
location. To make the measurements comparable throughout the dataset, we
adjusted all 1-minute radiometric values to the mean Sun - Earth
distance. Subsequently, we made all measurements relative to the Total
Solar Irradiance (TSI) at \(1 \text{au}\), in order to compensate for
the Sun's intensity variability, using a homogenized time series of
satellite TSI observations. The TSI data we use, is a combination of
data from NOAA \citep{Coddington2005} (for 1993-04-12 - 2023-03-31) and
adjusted data from \citet{TSIStsi} (for 2023-03-31 - 2023-05-31). As a
result, we can present all radiation data as a fraction of Sun's TSI.

@@

@@

\bibliography{/home/athan/LIBRARY/A\_Atmosphere/A\_Atmosphere.bib}

>>>>

The shortwave downward solar irradiance (SDR) at the Earth's surface
plays a significant role, on Earths climate. Changes of the SDR can be
related to major changes on the Earth's energy budget, the mechanisms of
climate change, and water and carbon cycle \citep{Wild2009}. Studies of
SDR variability, have identified some distinct SDR trends on different
regions of the world and for different time periods, using the term
`brightening' for positive trends, and `dimming' for negative trends.
There are many cases on the long term records, showing a change of SDR
trends direction, occurring roughly at the last decades of the 20th
century. \citet{Yang2021} reports a general dimming before 2000 and a
brightening afterwards on multiple station in China. \citet{Wild2021}
shows a similar pattern, with the breaking point around 1980 from a 71
years record of a Central Europe station and for Brazil by
\citet{Yamasoe2021}. Another approach, using AI aided spatial analysis
on continent level, of numerous observational stations data, reach
similar conclusions for the above regions and the global trend
\citep{Yuan2021}.

There is a consensus, among researchers, that the major factors of the
attenuation of SDR is the interaction with the atmospheric aerosols and
the clouds.

The interaction between Aerosols and clouds, among other factors, has
been analysed with modeling \citep{Li2016, Samset2018}, showing the
existence of feedback mechanisms between the two.

Similar links have been showed with observational data
{[}\citet{Ohvril2009}; \citet{Schwarz2020}; {]}

Due to the variability of those factors and the interaction between
them,

\ldots\ldots{} cloud formation occurrences and constitution nuclei.
cite\ldots..

it is difficult to estimate the SDR trends on each site.

Multiple studies attempt to evaluate the phenomenon and the potential
causes {[}; \citet{Wild2012}; \citet{Xia2007}; \citet{Zerefos2009}; and
references therein{]}.

Investigate multiple interaction \citet{Li2016} \citet{Samset2018} data
analysis and modeling

There is a also a need to evaluate the trends on different location

@@

A manual screening is performed, to remove inconsistencies and erroneous
recordings, that can occur randomly or systematically, during the long
continuous operation of the instrument. The manual screening is aided by
a radiation data quality assurance procedure, adjusted for this site,
based on methods of Long and Shi~\citetext{\citealp[
]{Long2008a}; \citealp{Long2006}}. Thus, problematic recordings have
been excluded from further processing. Although it is not possible to
detect all the bad data, the large number of data and the aggregation
scheme we use, can provide us with accurate radiometric measurements,
for the scope of this study.

@@

Due to a significant measurement uncertainty near, the horizon, we have
to exclude all measurements with SZA greater than \(85^\circ\).
Moreover, due to some obstructions around the site (hills and
buildings), we excluded data with Azimuth angle between \(35^\circ\) and
\(120^\circ\) with SZA greater than \(80^\circ\). On the latter
instances, Sun is systematically, not visible by the instrument's
location. To make the measurements comparable throughout the dataset, we
adjusted all 1-minute radiometric values to the mean Sun - Earth
distance. Subsequently, we made all measurements relative to the Total
Solar Irradiance (TSI) at \(1 \text{au}\), in order to compensate for
the Sun's intensity variability, using a homogenized time series of
satellite TSI observations. The TSI data we use, is a combination of
data from NOAA \citep{Coddington2005} (for 1993-04-12 - 2023-03-31) and
adjusted data from \citet{LASP2023} (for 2023-03-31 - 2023-05-31). As a
result, we can present all radiation data as a fraction of Sun's TSI.

@@

similar results with Evidence for Clear‐Sky Dimming and Brightening in
Central Europe\_Wild2021.pdf inclue in discusion

@@

\bibliography{Mainreferences.bib}

### 2023-06-29 Article_A.tex
Commit 2023-06-29 12:17

\title{Trends of SDR in Thessaloniki}
\author{true \and true}
\date{2023-06-26}

@@

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\hypertarget{introduction.}{%
\section{Introduction.}\label{introduction.}}

The shortwave downward solar irradiance (SDR) at the Earth's surface plays a significant role, on Earths climate.
Changes of the SDR can be related to major changes on factors affecting the radiative forcing balance and human activities.
Multiple studies attempt to evaluate the phenomenon and the potential causes (Ohvril et al. 2009; Schwarz et al. 2020; Wild 2009, 2012; Xia et al. 2007; Zerefos et al. 2009).
Although, there is regional variation of SDR, with both positive and negative trends, most of the studies agree that the major factors are the interaction of aerosols and clouds.

@@

A manual screening is performed, to remove inconsistencies and erroneous recordings, that can occur randomly or systematically, during the long continuous operation of the instrument.
The manual screening is aided by a radiation data quality assurance procedure, adjusted for this site, based on methods of Long and Shi~(2008, 2006).
Thus, problematic recordings have been excluded from further processing.
Although it is not possible to detect all the bad data, the large number of data and the aggregation scheme we use, can provide us with accurate radiometric measurements, for the scope of this study.

@@

As global radiation clear sky reference we are using the Haurwitz's model, adjusted for our site with a factor of 0.965 (Eq. \ref{eq:ahau}).
The selection of a clear sky reference model, was based on SDR observation from the period 2016 -- 2021.
Where, after an iterative optimization of eight simple models (Daneshyar--Paltridge--Proctor, Kasten--Czeplak, Haurwitz, Berger--Duffie, Adnot--Bourges--Campana--Gicquel, Robledo-Soler, Kasten and Ineichen-Perez) with different factors.
We found, that Haurwitz's model, adjusted with a factor of 0.965 has the lower root mean squared error (RMSE).
The tried models are described by Reno, Hansen, and Stein (2012) and tested by Reno and Hansen (2016).
The iterative optimization method, for the selection of the reference is discussed by Charles N. Long and Ackerman (2000) and Reno and Hansen (2016).

@@

In order to estimate the effect of the clouds on the SDR we created three datasets, by characterizing each one-minute measurement with a corresponding sky condition.
The all-sky conditions, containing all the valid measurements.
The clear-sky conditions data, where we have inferred that the sky was almost clear of clouds, and the remainder part the data as cloudy sky conditions data (cloud-sky).
To identify the clear-sky conditions we used the method proposed by Charles N. Long and Ackerman (2000) and by Reno and Hansen (2016), that was adapted and configured for the site.
We have to note, that the definition of what constitutes as clear or cloudy sky, has some subjectivity, due to the used method of characterization.
As a result, the details of the definition are site specific, it relies on a combination of threshold of comparisons with ideal actinometric models and statistics on different signal behavior.

@@

Due to a significant measurement uncertainty near, the horizon, we have to exclude
all measurements with SZA greater than \(85^\circ\).
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between
\(35^\circ\) and \(120^\circ\) with SZA greater than \(80^\circ\).
On the latter instances, Sun is systematically, not visible by the instrument's location.
To make the measurements comparable throughout the dataset, we adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at \(1 \text{au}\), in order to compensate for the Sun's intensity variability, using a homogenized time series of satellite TSI observations.
The TSI data we use, is a combination of data from NOAA (Coddington et al. 2005) (for 1993-04-12 - 2011-03-31) and adjusted data from LASP (n.d.) (for - ).
As a result, we can present all radiation data as a fraction of Sun's TSI.

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2048}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1928}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2169}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3855}}@{}}
\caption{\label{tab:trendtable}Trends of daily means by sky conditions.
}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule
\endhead
0.4221 & 5.871e-06 & All sky cond. & 100 \\
0.3871 & 0.0001123 & Clear sky cond. & 99.99 \\
0.415 & 0.002237 & Cloudy cond. & 99.78 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2361}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2222}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1250}}@{}}
\caption{\label{tab:trendseasontable}Trends of daily means by sky conditions for the seasons of the year. (continued below)}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Season
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Season
\end{minipage} \\
\midrule
\endhead
0.8014 & 0.1606 & All sky cond. & Winter \\
-0.1999 & 0.5397 & All sky cond. & Spring \\
0.2777 & 0.09127 & All sky cond. & Summer \\
0.3768 & 0.2006 & All sky cond. & Autumn \\
0.9574 & 0.1081 & Clear sky cond. & Winter \\
-0.4227 & 0.2207 & Clear sky cond. & Spring \\
0.0931 & 0.6638 & Clear sky cond. & Summer \\
0.3233 & 0.3255 & Clear sky cond. & Autumn \\
-0.4354 & 0.4924 & Cloudy cond. & Winter \\
0.8353 & 0.04263 & Cloudy cond. & Spring \\
0.7051 & 0.05457 & Cloudy cond. & Summer \\
0.3708 & 0.2357 & Cloudy cond. & Autumn \\
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{0.4444}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule
\endhead
83.94 \\
46.03 \\
90.87 \\
79.94 \\
89.19 \\
77.93 \\
33.62 \\
67.45 \\
50.76 \\
95.74 \\
94.54 \\
76.43 \\
\bottomrule
\end{longtable}

@@

Our result for all-sky condition (\(0.42\%/year\)), reaffirm the previous results of Bais et al. (2013) for the site.
The increase of this trend, shows that the phenomenon and probably the causes have been amplified.

\ldots..
Also, the trend of \(0.41\%/year\) for cloud-sky condition indicate the major part that clouds play on the
\ldots..

@@

\leavevmode\vadjust pre{\hypertarget{ref-Coddington2005}{}}%
Coddington, Odele, Judith L. Lean, Doug Lindholm, Peter Pilewskie amd Martin Snow, and NOAA CDR Program. 2005. {``{NOAA} Climate Data Record ({CDR}) of Total Solar Irradiance ({TSI}), {NRLTSI} Version 2. {D}aily.''} 2005. \url{https://doi.org/10.7289/V55B00C1}.

\leavevmode\vadjust pre{\hypertarget{ref-TSIStsi}{}}%
LASP. n.d. {``{TSIS-1} Total Solar Irradiance - Six Hour Average.''} Accessed June 1, 2023. \url{https://lasp.colorado.edu/tsis/data/}.

\leavevmode\vadjust pre{\hypertarget{ref-Long2006}{}}%
Long, C. N., and Y. Shi. 2006. {``The QCRad Value Added Product: Surface Radiation Measurement Quality Control Testing, Including Climatology Configurable Limits.''} DOE/SC-ARM/TR-074. Office of Science, Office of Biological; Environmental Research, U.S. Department of Energy.

\leavevmode\vadjust pre{\hypertarget{ref-long_automated_2008}{}}%
---------. 2008. {``An {Automated} {Quality} {Assessment} and {Control} {Algorithm} for {Surface} {Radiation} {Measurements}.''} \emph{The Open Atmospheric Science Journal}, 23--37.

\leavevmode\vadjust pre{\hypertarget{ref-Long2000}{}}%
Long, Charles N., and Thomas P. Ackerman. 2000. {``{Identification of clear skies from broadband pyranometer measurements and calculation of downwelling shortwave cloud effects}.''} \emph{Journal of Geophysical Research} 105 (D12): 15609--26. \url{https://doi.org/10.1029/2000JD900077}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Reno2016}{}}%
Reno, Matthew J., and Clifford W. Hansen. 2016. {``{Identification of periods of clear sky irradiance in time series of GHI measurements}.''} \emph{Renewable Energy} 90: 520--31. \url{https://doi.org/10.1016/j.renene.2015.12.031}.

@@

@@

@@

>>>>

\title{Trends of SDR in Thessaloniki}
\author{true \and true}
\date{2023-06-29}

@@

Cloud ``shrinking'' and ``optical thinning'' in the ``dimming'' period and a subsequent recovery in the ``brightening'' period over China

aerosols not only strengthen but also weaken the
growth of clouds with respect to their coverage and
optical thickness, depending on the levels of pollution
and the associated amounts of aerosols as postulated
in a conceptual framework (Wild 2009a, 2012, Yang
et al 2012).

\hypertarget{introduction.}{%
\section{Introduction.}\label{introduction.}}

The shortwave downward solar irradiance (SDR) at the Earth's surface plays a significant role, on Earths climate.
Changes of the SDR can be related to major changes on the Earth's energy budget, the mechanisms of climate change, and water and carbon cycle (Wild 2009).
Studies of SDR variability, have identified some distinct SDR trends on different regions of the world and for different time periods, using the term `brightening' for positive trends, and `dimming' for negative trends.
There are many cases on the long term records, showing a change of SDR trends direction, occurring roughly at the last decades of the 20th century.
Yang et al. (2021) reports a general dimming before 2000 and a brightening afterwards on multiple station in China.
Wild et al. (2021) shows a similar pattern, with the breaking point around 1980 from a 71 years record of a Central Europe station and for Brazil by Yamasoe et al. (2021).
Another approach, using AI aided spatial analysis on continent level, of numerous observational stations data, reach similar conclusions for the above regions and the global trend (Yuan, Leirvik, and Wild 2021).

There is a consensus, among researchers, that the major factors of the attenuation of SDR is the interaction with the atmospheric aerosols and the clouds.

The interaction between Aerosols and clouds, among other factors, has been analysed with modeling (Li et al. 2016; Samset et al. 2018), showing the existence of feedback mechanisms between the two.

Similar links have been showed with observational data {[}Ohvril et al. (2009); Schwarz et al. (2020); {]}

Due to the variability of those factors and the interaction between them,

\ldots\ldots{} cloud formation occurrences and constitution nuclei. cite\ldots..

it is difficult to estimate the SDR trends on each site.

Multiple studies attempt to evaluate the phenomenon and the potential causes {[}; Wild (2012); Xia et al. (2007); Zerefos et al. (2009); and references therein{]}.

Investigate multiple interaction Li et al. (2016) Samset et al. (2018) data analysis and modeling

There is a also a need to evaluate the trends on different location

@@

A manual screening is performed, to remove inconsistencies and erroneous recordings, that can occur randomly or systematically, during the long continuous operation of the instrument.
The manual screening is aided by a radiation data quality assurance procedure, adjusted for this site, based on methods of Long and Shi~(C. Long and Shi 2008 ; C. Long and Shi 2006).
Thus, problematic recordings have been excluded from further processing.
Although it is not possible to detect all the bad data, the large number of data and the aggregation scheme we use, can provide us with accurate radiometric measurements, for the scope of this study.

@@

As global radiation clear sky reference we are using the Haurwitz's model, adjusted for our site with a factor of 0.965 (Eq. \ref{eq:ahau}).
The selection of a clear sky reference model, was based on SDR observation from the period 2016 -- 2021.
Where, after an iterative optimization of eight simple models (Daneshyar--Paltridge--Proctor, Kasten--Czeplak, Haurwitz, Berger--Duffie, Adnot--Bourges--Campana--Gicquel, Robledo-Soler, Kasten and Ineichen-Perez) with different factors.
We found, that Haurwitz's model, adjusted with a factor of 0.965 has the lower root mean squared error (RMSE).
The tried models are described by Reno, Hansen, and Stein (2012) and tested by Reno and Hansen (2016).
The iterative optimization method, for the selection of the reference is discussed by C. N. Long and Ackerman (2000) and Reno and Hansen (2016).

@@

In order to estimate the effect of the clouds on the SDR we created three datasets, by characterizing each one-minute measurement with a corresponding sky condition.
The all-sky conditions, containing all the valid measurements.
The clear-sky conditions data, where we have inferred that the sky was almost clear of clouds, and the remainder part the data as cloudy sky conditions data (cloud-sky).
To identify the clear-sky conditions we used the method proposed by C. N. Long and Ackerman (2000) and by Reno and Hansen (2016), that was adapted and configured for the site.
We have to note, that the definition of what constitutes as clear or cloudy sky, has some subjectivity, due to the used method of characterization.
As a result, the details of the definition are site specific, it relies on a combination of threshold of comparisons with ideal actinometric models and statistics on different signal behavior.

@@

Due to a significant measurement uncertainty near, the horizon, we have to exclude
all measurements with SZA greater than \(85^\circ\).
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between
\(35^\circ\) and \(120^\circ\) with SZA greater than \(80^\circ\).
On the latter instances, Sun is systematically, not visible by the instrument's location.
To make the measurements comparable throughout the dataset, we adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at \(1 \text{au}\), in order to compensate for the Sun's intensity variability, using a homogenized time series of satellite TSI observations.
The TSI data we use, is a combination of data from NOAA (Coddington et al. 2005) (for 1993-04-12 - 2023-03-31) and adjusted data from LASP (2023) (for 2023-03-31 - 2023-05-31).
As a result, we can present all radiation data as a fraction of Sun's TSI.

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2048}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1928}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2169}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3855}}@{}}
\caption{\label{tab:trendtable}Trends of daily means by sky conditions.
}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule
\endhead
0.381 & 3.479e-21 & All sky cond. & 100 \\
0.3605 & 1.068e-16 & Clear sky cond. & 100 \\
0.3472 & 8.968e-09 & Cloudy cond. & 100 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2361}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2222}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1250}}@{}}
\caption{\label{tab:trendseasontable}Trends of daily means by sky conditions for the seasons of the year. (continued below)}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Season
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\centering
Trend {[}\%/year{]}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Trend p-value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sky condition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Season
\end{minipage} \\
\midrule
\endhead
0.7215 & 0.001209 & All sky cond. & Winter \\
0.1679 & 0.1083 & All sky cond. & Spring \\
0.128 & 0.08705 & All sky cond. & Summer \\
0.4239 & 0.006659 & All sky cond. & Autumn \\
0.8715 & 0.000269 & Clear sky cond. & Winter \\
0.09719 & 0.3923 & Clear sky cond. & Spring \\
-0.02369 & 0.7972 & Clear sky cond. & Summer \\
0.3583 & 0.02996 & Clear sky cond. & Autumn \\
-0.02581 & 0.9335 & Cloudy cond. & Winter \\
0.3557 & 0.06914 & Cloudy cond. & Spring \\
0.442 & 0.004988 & Cloudy cond. & Summer \\
0.4776 & 0.01955 & Cloudy cond. & Autumn \\
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{0.4444}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
Trend statistical signif. {[}\%{]}
\end{minipage} \\
\midrule
\endhead
99.88 \\
89.17 \\
91.29 \\
99.33 \\
99.97 \\
60.77 \\
20.28 \\
97 \\
6.646 \\
93.09 \\
99.5 \\
98.04 \\
\bottomrule
\end{longtable}

@@

Our result for all-sky condition (\(0.38\%/year\)), reaffirm the previous results of Bais et al. (2013) for the site.
The increase of this trend, shows that the phenomenon and probably the causes have been amplified.

\ldots..
Also, the trend of \(0.35\%/year\) for cloud-sky condition indicate the major part that clouds play on the
\ldots..

@@

\leavevmode\vadjust pre{\hypertarget{ref-Coddington2005}{}}%
Coddington, Odele, Judith L. Lean, Doug Lindholm, Peter Pilewskie, Martin Snow, and NOAA CDR Program. 2005. {``{NOAA} Climate Data Record ({CDR}) of Total Solar Irradiance ({TSI}), {NRLTSI} Version 2. {D}aily.''} 2005. \url{https://doi.org/10.7289/V55B00C1}.

\leavevmode\vadjust pre{\hypertarget{ref-LASP2023}{}}%
LASP. 2023. {``TSIS-1 Total Solar Irradiance - Six Hour Average.''} Laboratory for Atmospheric; Space Physics, University of Colorado, Boulder. 2023. \url{https://lasp.colorado.edu/tsis/data/}.

\leavevmode\vadjust pre{\hypertarget{ref-Li2016}{}}%
Li, Zhanqing, W. K.‐M. Lau, V. Ramanathan, G. Wu, Y. Ding, M. G. Manoj, J. Liu, et al. 2016. {``Aerosol and Monsoon Climate Interactions over Asia.''} \emph{Reviews of Geophysics} 54 (4): 866--929. \url{https://doi.org/10.1002/2015RG000500}.

\leavevmode\vadjust pre{\hypertarget{ref-Long2000}{}}%
Long, Charles N., and Thomas P. Ackerman. 2000. {``Identification of Clear Skies from Broadband Pyranometer Measurements and Calculation of Downwelling Shortwave Cloud Effects.''} \emph{Journal of Geophysical Research: Atmospheres} 105 (D12, D12): 15609--26. \url{https://doi.org/10.1029/2000jd900077}.

\leavevmode\vadjust pre{\hypertarget{ref-Long2006}{}}%
Long, C., and Y. Shi. 2006. {``The QCRad Value Added Product: Surface Radiation Measurement Quality Control Testing, Including Climatology Configurable Limits.''} DOE/SC-ARM/TR-074. Office of Science, Office of Biological; Environmental Research, U.S. Department of Energy.

\leavevmode\vadjust pre{\hypertarget{ref-Long2008a}{}}%
---------. 2008. {``An Automated Quality Assessment and Control Algorithm for Surface Radiation Measurements.''} \emph{The Open Atmospheric Science Journal}, 23--37.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Reno2016}{}}%
Reno, Matthew J., and Clifford W. Hansen. 2016. {``Identification of Periods of Clear Sky Irradiance in Time Series of GHI Measurements.''} \emph{Renewable Energy} 90: 520--31. \url{https://doi.org/gq3sbg}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Samset2018}{}}%
Samset, B. H., M. Sand, C. J. Smith, S. E. Bauer, P. M. Forster, J. S. Fuglestvedt, S. Osprey, and C.‐F. Schleussner. 2018. {``Climate Impacts from a Removal of Anthropogenic Aerosol Emissions.''} \emph{Geophysical Research Letters} 45 (2): 1020--29. \url{https://doi.org/10.1002/2017GL076079}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Wild2021}{}}%
Wild, Martin, Stephan Wacker, Su Yang, and Arturo Sanchez‐Lorenzo. 2021. {``Evidence for Clear‐sky Dimming and Brightening in Central Europe.''} \emph{Geophysical Research Letters} 48 (6). \url{https://doi.org/10.1029/2020GL092216}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Yamasoe2021}{}}%
Yamasoe, Marcia Akemi, Nilton Manuel Évora Rosário, Samantha Novaes Santos Martins Almeida, and Martin Wild. 2021. {``Fifty-Six Years of Surface Solar Radiation and Sunshine Duration over São Paulo, Brazil: 1961--2016.''} \emph{Atmospheric Chemistry and Physics} 21 (9): 6593--603. \url{https://doi.org/10.5194/acp-21-6593-2021}.

\leavevmode\vadjust pre{\hypertarget{ref-Yang2021}{}}%
Yang, Su, Zijiang Zhou, Yu Yu, and Martin Wild. 2021. {``Cloud {`Shrinking'} and {`Optical Thinning'} in the {`Dimming'} Period and a Subsequent Recovery in the {`Brightening'} Period over China.''} \emph{Environmental Research Letters}, January. \url{https://doi.org/10.1088/1748-9326/abdf89}.

\leavevmode\vadjust pre{\hypertarget{ref-Yuan2021}{}}%
Yuan, Menghan, Thomas Leirvik, and Martin Wild. 2021. {``Global Trends in Downward Surface Solar Radiation from Spatial Interpolated Ground Observations During 1961-2019.''} \emph{Journal of Climate}, September, 1--56. \url{https://doi.org/10.1175/JCLI-D-21-0165.1}.
